\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-19 paper1.tex
removed a/j tuning algorithm and simply stated it textually

Consider, as a starting point, the case in which a vehicle is moving at some small initial speed and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:full7phasespec} shows this trajectory over time.
The problem is defined by the vector of known values $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
It is assume that the final forward acceleration will be zero.
If the magnitude of the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The remaining parameters yet to be set now become $\mathbf{a}_m = [a^+_m , a^-_m]$ and $\mathbf{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.
As we will show later, peak acceleration and jerk must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
This is computed for every point along the path.
In the simplest case, one value for each of the quantities expressed in those relations may be chosen for the entire path.

@@

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$. All impossible scenarios are automatically ruled out.
To find closed-form solutions for each, a symbolic solver was used. The target values for each profile are the time steps between jerk changes.
These are solved by plugging in initial conditions, default jerk values

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in negative time intervals for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Algorithm \ref{alg:modifyacceljerkpeaks} describes this procedure.
When it fails, a new jerk profile must be chosen.

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{ModifyAccelJerkPeaks}{$\Delta t$, $\mathbf{a}_m$, $\mathbf{j}_m$, $\mathbf{a}^{max}_m$, $\mathbf{j}^{max}_m$}

    \EndProcedure
  \end{algorithmic}
\caption{Procedure for modifying peak accel and jerk magnitude for rememdy negative time intervals for a given phase. This procedure is employed for each of the profiles.}
\label{alg:modifyacceljerkpeaks}
\end{figure}

>>>>

Consider, as a starting point, the case in which a vehicle is moving at some small initial speed and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:full7phasespec} shows this trajectory over time.
The problem is defined by the vector of known values $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
It is assume that the final forward acceleration will be zero.
If the magnitude of the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The remaining parameters yet to be set now become $\mathbf{a}_m = [a^+_m , a^-_m]$ and $\mathbf{j}_m = [j^+_m , j^-_m]$.
As we will show later, peak acceleration and jerk must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
This is computed for every point along the path.
In the simplest case, one value for each of the quantities expressed in those relations may be chosen for the entire path.

@@

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$.
All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, travelling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that travelling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for each, a symbolic solver was used.
The target values for each profile are the time steps between jerk changes.
These are solved by plugging in $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$.

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in a negative time interval for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Specifically, jerk may be increased while peak acceleration is decreased.
If no acceptable values are found within the valid ranges of $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$, a new jerk profile must be chosen.
